---
title: "10_import"
output: html_notebook
---

# Metro Interstate Traffic Volume Data

### Data Set Information

Hourly Interstate 94 Westbound traffic volume for MN DoT ATR station 301, roughly midway between Minneapolis and St Paul, MN. Hourly weather features and holidays included for impacts on traffic volume.


### Attribute Information

holiday: Categorical US National holidays plus regional holiday, Minnesota State Fair
temp: Numeric Average temp in kelvin
rain_1h: Numeric Amount in mm of rain that occurred in the hour
snow_1h: Numeric Amount in mm of snow that occurred in the hour
clouds_all: Numeric Percentage of cloud cover
weather_main: Categorical Short textual description of the current weather
weather_description: Categorical Longer textual description of the current weather
date_time: DateTime Hour of the data collected in local CST time
traffic_volume: Numeric Hourly I-94 ATR 301 reported westbound traffic volume


### Motivating question
What are good predictors of when traffic will have the greatest volume?


I will need the following libraries:

```{r libraries}
library(readxl)
library(assertr)
library(dplyr)
library(purrr)
library(janitor)
library(lubridate)
library(tidyr)
```


Now, I will load the data and examine it.
```{r load data}
Metro_Traffic <- read_excel("Metro_Interstate_Traffic_Volume.xlsx") %>%
  clean_names()

head(Metro_Traffic)

Metro_Traffic %>%
  map(class)

```

Before we delve too deeply in the data, we want to make sure there is no abnormal data in the dataset. To do so, we will use the assertr library to check different variables. 

First, let's make sure that the variable measuring cloud cover (in percent) lies between 0 and 100. 

```{r check cloud coverage}
Metro_Traffic %>%
  assert(within_bounds(0, 100), clouds_all)
```

Looks good! 

Let's also look at temperature values. The temperature variable looks very high! This is because the temps are in kelvin. We want to convert them to Fahrenheit so that they are more meaningful. I will do this first before testing them. 
```{r convert temperature}
Metro_Traffic1 <- Metro_Traffic %>%
  mutate(temp_f = (((temp - 273.15) * 9) / 5)  + 32) %>%
  arrange(temp_f)
Metro_Traffic1
```

Now, let's test this new variable. 
```{r test temperature}
Metro_Traffic1 %>%
  assert(within_bounds(-45, 110), temp_f)
```

There were 10 values in the dataset with temperatures listed at -459 degrees. This is definitely incorrect.

I will label these values as 'NA.'
```{r fix incorrect data}
Metro_Traffic1 %>% 
  mutate(temp_f = replace(temp_f, temp_f<= -45, NA))
```


Normally, I would also want to change the date and time to the correct format but, in this case, they already are.

```{r check date and time}
str(Metro_Traffic$date_time)
min(Metro_Traffic$date_time)
max(Metro_Traffic$date_time)
```


