---
title: "30_feature_engineering"
output: html_notebook
---

# Adding features to the existing dataset

First, I will standardize the rain variable to compare all amounts of rain in a given hour to the mean. Rain and other precipitation may have an impact on traffic volume.
```{r create feature function 1}
scale2 <- function(x) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)
scaled_rain <- function(df, var){
  df %>% 
  mutate_at({{var}}, list(std_rain = scale2))
  }
```

I will now transform the holiday variable to be binary. 0 will denote a non-holiday day and 1 will be a holiday. It would be useful to compare the traffic on days that are traditionally celebrated as holidays versus non-holidays
```{r create feature function 2}
holiday_new <- function(x) (ifelse(x == "None", 0, 1))
holiday_function <- function(df, var) {
  df %>%
  mutate_at({{var}}, list(holiday_binary = holiday_new))
    
}
```

It would be useful to also add a column specifying the day of the week. Day of week may have an impact on the traffic volume especially comparing weekdays to weekend days.
```{r create feature function 3}
weekday <- function(x) (wday(x, label = TRUE))
weekday_function <- function(df, var) {
  df %>%
    mutate_at({{var}}, list(day_of_week = weekday))
}
```

I also want to make a rush hour variable. In this instance, this will only be for the morning hours which I will assume are between 7 and 9. I believe that this would be a good indicator of how much traffic will be present compared to non-rush hour volume.
```{r create feature function 4}
time1 <- ymd_hms("2012-10-02 07:00:00")
time2 <- ymd_hms("2018-09-30 09:00:00")
rush_hour1 <- function(x) (x %in% interval(time1, time2))
rush_hour_function <- function(df, var) {
    df %>%
    mutate_at({{var}}, list(am_rush_hour = rush_hour1))
}
```


I will now add all of the new features to the data frame in order to prepare for modelling.
```{r add features to data}
Metro_Traffic_eng <- Metro_Traffic1 %>%
  scaled_rain("rain_1h") %>%
  holiday_function("holiday") %>%
  weekday_function("date_time") %>%
  rush_hour_function("date_time") %>%
  select(traffic_volume, everything())
```


I will test all of my new variables now to determine if they are working properly.

```{r test std_rain}
Metro_Traffic_eng %>%
  assert(within_bounds(-4, 4), std_rain)

```

I will remove this value since it lies so far from the acceptable range.

```{r fix std_rain}
Metro_Traffic_eng %>%
  mutate(std_rain = replace(std_rain, std_rain > 4, NA))
```

I want to also make sure that the binary version of the holiday variable is 0 or 1.
```{r test holiday}
Metro_Traffic_eng %>%
  assert(within_bounds(0,1), holiday_binary) 
```


